diffEnrich: An \proglang{R} Package to Compare Functional Enrichment Between Two Experimentally-derived Groups of Genes by Connecting to the KEGG REST API

### 2019-11-15 jss-article-rnw-diffEnrich/article.Rnw
Started subsection 2.1 in article.Rnw

>>>>

\medskip

You can install the released version of diffEnrich from CRAN with:

<<installation, echo=TRUE, eval=FALSE>>=
install.packages("diffEnrich")
@

\subsection{\code{get\textunderscore kegg}: Download and prepare pathways from KEGG API}

First, the \code{get\textunderscore kegg} function is used to connect to the
KEGG REST API and download the data sets required to perform downstream
analysis. Currently, this function supports three species: Homo sapiens, Mus
musculus, and Rattus norvegicus. For a given species, three data sets are
generated: 1) ncbi\textunderscore to\textunderscore kegg: this data set maps NCBI/ENTREZ gene IDs to KEGG gene
IDs, 2) kegg\textunderscore to\textunderscore pathway: this data set maps KEGG gene IDs to their respective
KEGG pathway IDs, and 3) pathway\textunderscore to\textunderscore species: this data set maps KEGG pathway IDs
to their respective pathway descriptions. This function allows the user to save
versioned (based on KEGG release) and time-stamped text files of the three data
sets described above. In addition to these flat files, \code{get\textunderscore kegg} will also create
a named list in R with the three data sets. \code{get\textunderscore kegg} can also read in the saved
text files from a past run and format them for downstream analyses. This
function typically completes in a few seconds, but it is important to note that
the finishing time is dependent on the time it takes to connect to the KEGG API.

### 2019-11-15 jss-article-rnw-diffEnrich/article.tex
Started subsection 2.1 in article.Rnw

>>>>

\medskip

You can install the released version of diffEnrich from CRAN with:

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{install.packages}\hlstd{(}\hlstr{"diffEnrich"}\hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

\subsection{\code{get\textunderscore kegg}: Download and prepare pathways from KEGG API}

First, the \code{get\textunderscore kegg} function is used to connect to the
KEGG REST API and download the data sets required to perform downstream
analysis. Currently, this function supports three species: Homo sapiens, Mus
musculus, and Rattus norvegicus. For a given species, three data sets are
generated: 1) ncbi\textunderscore to\textunderscore kegg: this data set maps NCBI/ENTREZ gene IDs to KEGG gene
IDs, 2) kegg\textunderscore to\textunderscore pathway: this data set maps KEGG gene IDs to their respective
KEGG pathway IDs, and 3) pathway\textunderscore to\textunderscore species: this data set maps KEGG pathway IDs
to their respective pathway descriptions. This function allows the user to save
versioned (based on KEGG release) and time-stamped text files of the three data
sets described above. In addition to these flat files, \code{get\textunderscore kegg} will also create
a named list in R with the three data sets. \code{get\textunderscore kegg} can also read in the saved
text files from a past run and format them for downstream analyses. This
function typically completes in a few seconds, but it is important to note that
the finishing time is dependent on the time it takes to connect to the KEGG API.
